---
title: "How to create a US map with color indication"
author: "Huawen Sun"
date: "2019/06/05"
output: html_document
---
```{r setup, include = FALSE}
library(data.table)
library(usmap)
library(ggplot2)
```

```{r echo = FALSE}
TopData <- fread("./data/State_MedianListingPrice_TopTier.csv")
colnames(TopData)[1] <- "state"
```

## Packages needed:

####ggplot2
####usmap

## Data needed:
Any data with state names will work for this plot, but the column name for the state names
must be 'state' or 'fips'.
For example, I am using a US home sale price data for all states, which contains
state names.

## Creating the basic map
First step is to create a basic map that uses value as color indication.

For example:

```
plot_usmap(data = TopData, values = "10-Jan", lines = "white")

```

```{r echo = FALSE}
plot_usmap(data = TopData, values = "10-Jan", lines = "white")
```

It will create a US map, and uses price in Jan 2010 as color indication. The more expensive the price is, 
the color will be darker.
You can also see that each state is separated by white lines, you can also change the color of the lines to
other colors. For example, red lines.

```
plot_usmap(data = TopData, values = "10-Jan", lines = "red")
```
```{r echo = FALSE}
plot_usmap(data = TopData, values = "10-Jan", lines = "red")
```

Now the color of lines are red.

## Add legend

To add legend, you can use

```
scale_fill_continuous(name = "price of 2010-01", label = scales::comma)
```
We are naming the legend as 'price of 2010-01', and set the scale of legend color to the price values.

```{r echo = FALSE}
plot_usmap(data = TopData, values = "10-Jan", lines = "white") + 
  scale_fill_continuous(name = "price of 2010-01", label = scales::comma)
```

If you want to change the postion of the legend, you can type:
```
theme(legend.position = "right")
```

```{r echo = FALSE}
plot_usmap(data = TopData, values = "10-Jan", lines = "white") + 
  scale_fill_continuous(name = "price of 2010-01", label = scales::comma) + 
  theme(legend.position = "right")
```

Now the legend is placed at the right side of the map.

## Add titles
You can also add title and subtitle to the map.
```
labs(title = "US home sale price 01/2010", subtitle = "Color indicates the price")
```
```{r echo = FALSE}
plot_usmap(data = TopData, values = "10-Jan", lines = "white") + 
  scale_fill_continuous(name = "price of 2010-01", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(title = "US home sale price 01/2010", subtitle = "Color indicates the price")
```

## Complete Code
```
library(data.table)
library(usmap)
library(ggplot2)

TopData <- fread("./data/State_MedianListingPrice_TopTier.csv")

colnames(TopData)[1] <- "state"

plot_usmap(data = TopData, values = "10-Jan", lines = "white") + 
  scale_fill_continuous(name = "price of 2010-01", label = scales::comma) + 
  theme(legend.position = "right") +
  labs(title = "US home sale price 01/2010", subtitle = "Color indicates the price")
```
## Thank you for reading!

## Part of TopData
### State name and 2010-01 price

```{r echo = FALSE}
TopData$state
TopData$`10-Jan`
```